### 2022-01-10 input/related_work.tex
adapting to two columns, stilltodo. simpler problem display
few fixes, add physarum to biblio
physarum related work

Content indexing services in geo-distributed infrastructures allow
\processes to retrieve specific content while leveraging the
advantages of replication. These systems mostly rely on dedicated
location services hosted by possibly remote third-party \processes; but
cutting out the middleman requires that each \process maintains its
own index in a decentralized fashion.

@@

\noindent The most closely related approaches to \NAME come from
\underline{i}nformation-\underline{c}entric \underline{n}etworking
(ICN)~\cite{garcia-lopez, hemmati2015namebased}. They periodically
advertise their cache content, and advertisements stop as soon as they
reach uninterested \processes. However their operation requires that
\begin{inparaenum}[(i)]
\item they constantly generate traffic even in quiescent systems where
  \processes do not add nor destroy replicas; and 
\item they define physical-clock-based timeouts the value of which
  depends on network topology properties such as network diameter.
  %also incur an overhead even in quiet contexts without any update.
  % Moreover, they necessarily rely on physical timeouts
  Unfitting timeouts lead to premature removals of live replicas; or
  slow convergence where \processes wrongly believe that their closest
  replica is live while it was destroyed.
\end{inparaenum}
On the opposite, \NAME quickly informs each \process of its closest
replica even in large networks; % when the system is quiescent,
and has no overhead when the system is quiescent.

>>>>

\TODO{Vector routing protocols.} 
Content indexing services in geo-distributed infrastructures allow
\processes to retrieve specific content while leveraging the
advantages of replication. These systems mostly rely on dedicated
location services hosted by possibly remote third-party \processes; but
cutting out the middleman requires that each \process maintains its
own index in a decentralized fashion.

@@

\noindent The most closely related approaches to \NAME come from
\underline{i}nformation-\underline{c}entric \underline{n}etworking
(ICN)~\cite{garcia-lopez, hemmati2015namebased} and distributed
clustering~\cite{sohier2012physarum}. The sources advertise themselves
periodically. Advertisements either stop as soon as they reach
uninterested \processes~\cite{garcia-lopez, hemmati2015namebased}, or
probabilistically propagate through most likely interested
\processes~\cite{sohier2012physarum}. However their operation requires
that
\begin{inparaenum}[(i)]
\item they constantly generate traffic even in quiescent systems where
  \processes do not add nor destroy replicas; and 
\item they either operate in synchronous
  systems~\cite{sohier2012physarum} or must define
  physical-clock-based timeouts the value of which depends on network
  topology properties such as network diameter~\cite{garcia-lopez,
    hemmati2015namebased}.
  %also incur an overhead even in quiet contexts without any update.
  % Moreover, they necessarily rely on physical timeouts
  Unfitting timeouts lead to premature removals of live replicas; or
  slow convergence where \processes wrongly believe that their closest
  replica is live while it was destroyed.
\end{inparaenum}
On the opposite, \NAME quickly informs each \process of its closest
replica even in large and dynamic networks with asynchronous
communications; and has no overhead when the system is quiescent.
